decompr: GVC decomposition in R

### 2015-03-10 draft.Rnw
readd front page, CTEI version renamed

>>>>

\maketitle

\vspace{\stretch{1}}
\abstract{Global Value Chains have become a central unit of analysis in research on international trade.
However, the complex matrix transformations at the basis of most Value Chain indicators still constitute a significant entry barrier to
the field.
The R package decompr solves this problem by implementing the algorithms for the analysis of Global Value Chains as R procedures, thereby simplifying the decomposition process.
Two methods for gross export flow decomposition using Inter-Country Input-Output tables are provided.
The first method concerns a decomposition based on the classical \textcite{wale36} insight.
It derives the value added origins of an industry's exports by source country and source industry, using easily vailable gross trade data.
The second method is the Wang-Wei-Zhu algorithm which splits bilateral gross exports into 16 value added components. 
These components can broadly be divided into domestic and foreign value added in exports.
Using the results of the two decompositions, decompr provides a set of Global Value Chain indicators, such as the now standard Vertical Specialisation ratio.
This article summarises the methodology of the algorithms, describes the format of the input and output data, 
and exemplifies the usefulness of the two methods on the basis of a simple example data set.}
\pagebreak

### 2015-03-10 draft.tex
readd front page, CTEI version renamed

\hlcom{# inspect the content of the decompr object}
\hlkwd{ls}\hlstd{(decompr_object)}
\end{alltt}
\begin{verbatim}
##  [1] "A"         "Ad"        "Am"        "B"         "Bd"       
##  [6] "bigrownam" "Bm"        "E"         "Efd"       "Eint"     
## [11] "ESR"       "Exp"       "G"         "GN"        "k"        
## [16] "L"         "N"         "rownam"    "tot"       "Vc"       
## [21] "Vhat"      "X"         "Y"         "Yd"        "Ym"       
## [26] "z"         "z01"       "z02"       "z1"        "z2"
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\hlcom{# inspect the content of the decompr object}
\hlkwd{ls}\hlstd{(decompr_object)}
\end{alltt}
\begin{verbatim}
##  [1] "A"         "Ad"        "Am"        "B"         "Bd"       
##  [6] "bigrownam" "Bm"        "E"         "Efd"       "Eint"     
## [11] "ESR"       "Exp"       "G"         "GN"        "i"        
## [16] "k"         "L"         "N"         "rownam"    "Vc"       
## [21] "Vhat"      "X"         "Y"         "Yd"        "Ym"       
## [26] "z"         "z01"       "z02"
\end{verbatim}
\end{kframe}
\end{knitrout}
